Layered Formal Verification of a TCP Stack

### 2021-06-03 SecDev21/paper.tex
Uniformize the figures style

\begin{figure}
\begin{lstlisting}[language=Ada,basicstyle=\footnotesize\ttfamily]
procedure Socket_Connect
   (Sock           : in out Not_Null_Socket;
    Remote_Ip_Addr : in     IpAddr;
    Remote_Port    : in     Port;
    Error          :    out Error_T)
   with
   Pre => Is_Initialized_Ip (Remote_Ip_Addr),
   Post =>
    if Sock.S_Type = SOCKET_TYPE_STREAM then
      (if Error = NO_ERROR then
        Sock.S_Remote_Ip_Addr = Remote_Ip_Addr)
    else
      Sock.S_Remote_Ip_Addr = Remote_Ip_Addr

@@

\begin{lstlisting}[language=Ada, basicstyle=\footnotesize\ttfamily,
                    numbers=left, numberstyle=\tiny, escapechar=\%]
case Sock.State is
  when TCP_STATE_SYN_RECEIVED
     | TCP_STATE_ESTABLISHED =>
  -- Flush the send buffer
  TCP_Send (Sock, Buf, Ignore_Written,
            SOCKET_FLAG_NO_DELAY, Error);
  if Error /= NO_ERROR then
      return;
  end if;

>>>>

\begin{figure}
\begin{lstlisting}[language=Ada,basicstyle=\footnotesize\ttfamily, frame=bottomline]
procedure Socket_Connect
   (Sock           : in out Not_Null_Socket;
    Remote_Ip_Addr : in     IpAddr;
    Remote_Port    : in     Port;
    Error          :    out Error_T)
   with
   Pre => Is_Initialized_Ip (Remote_Ip_Addr),
   Post =>
    if Sock.S_Type = SOCKET_TYPE_STREAM then
      (if Error = NO_ERROR then
        Sock.S_Remote_Ip_Addr = Remote_Ip_Addr)
    else
      Sock.S_Remote_Ip_Addr = Remote_Ip_Addr

@@

\begin{lstlisting}[language=Ada, basicstyle=\footnotesize\ttfamily,
                    numbers=left, numberstyle=\tiny, escapechar=\%,
                    numbersep=0pt]
case Sock.State is
  when TCP_STATE_SYN_RECEIVED
     | TCP_STATE_ESTABLISHED =>
  -- Flush the send buffer
  TCP_Send (Sock, Buf, Ignore_Written,
            SOCKET_FLAG_NO_DELAY, Error);
  if Error /= NO_ERROR then
      return;
  end if;
